Simulations, CLT and EVT

### 2020-08-27 mean_null.Rmd
delete dsitribution

```{r max_small_lev}
set.seed(12345)
plot_simdata(nlevels = seq(2, 10, 1),
             nsim = 500, 
             create_fun = max)
```

@@

```{r max_large_lev}
set.seed(54321)
plot_simdata(nlevels = seq(20, 45, 5),
             nsim = 500, 
             create_fun = max)
```

```{r norm_max}
# normalised maximum of a vector
norm_max <- function(x = NULL){
      nx <- length(x)
      p = 1-(1/nx)
      shape = 0.5
      rate = 3
      meanx = shape/rate
      sdx = shape/(rate^2)
      b = stats::qnorm(p, meanx, sdx)
      a = 1/(nx*stats::dnorm(b, meanx, sdx))
      #k = stats::quantile(x, p, type = 8, na.rm = TRUE)
      (max(x) - a)/b
      #max(x)/k
      }
```

@@

```{r normmax_small_lev}
set.seed(12345)
plot_simdata(nlevels = seq(2, 10, 1),
             nsim = 500, 
             create_fun = norm_max,
             distr = "gumbel")
```

@@

```{r normmax_large_lev}
set.seed(54321)
plot_simdata(nlevels = seq(20, 45, 5),
             nsim = 500, 
             create_fun = norm_max, 
             distr = "gumbel")
```

>>>>

```{r max_small_lev}
set.seed(12345)
plot_simdata(nlevels = seq(2, 10, 1),
             nsim = 500, 
             create_fun = max,
               sim_dist = distributional::dist_normal(5, 10),
             distr = "gumbel")
```

@@

```{r max_large_lev}
set.seed(54321)
plot_simdata(nlevels = seq(20, 45, 5),
             nsim = 500, 
             create_fun = max,
               sim_dist = distributional::dist_normal(5, 10),
             distr = "gumbel")
```

```{r norm_max}
# normalised maximum of a vector
norm_max <- function(x = NULL){
      nx <- length(x)
      p = 1-(1/nx)
      shape = 0.5
      rate = 3
      # meanx = shape/rate
      # sdx = shape/(rate^2)
      meanx = 5
      sdx = 10
      b = stats::qnorm(p, meanx, sdx)
      a = 1/(nx*stats::dnorm(b, meanx, sdx))
      #k = stats::quantile(x, p, type = 8, na.rm = TRUE)
      (max(x) - a)/b
      #max(x)/k
      }
```

@@

```{r normmax_small_lev}
set.seed(12345)
plot_simdata(nlevels = seq(2, 10, 1),
             nsim = 500, 
             sim_dist = distributional::dist_normal(5, 10),
             create_fun = norm_max,
             distr = "gumbel")
```

@@

```{r normmax_large_lev}
set.seed(54321)
plot_simdata(nlevels = seq(20, 45, 5),
             nsim = 500, 
             create_fun = norm_max, 
             sim_dist = distributional::dist_normal(5, 10),
             distr = "gumbel")
```
